Earth's Impact History and the Timing of the Origin of Life

### 2023-04-19 ms.tex
period

The timing of an origin of life impact is qualitatively unchanged when instead adopting the \citet{Wogan_2023} pessimistic case, which requires a $> 5 \times 10^{21}$ kg impact without later ocean vaporization (Figure \ref{fig:time_and_mass}b). In this scenario, the median timing for life's origin is 4.36 Ga with 95\% a confidence interval spanning 3.94 to 4.49 Ga (Figure \ref{fig:time_and_mass}b (i)). Under these assumptions, the life-starting impact is Moneta-sized 31\% of the time (Figure \ref{fig:time_and_mass}b (ii)), which is more probable compared to ``optimistic'' case (Figure \ref{fig:time_and_mass}a (ii))

>>>>

The timing of an origin of life impact is qualitatively unchanged when instead adopting the \citet{Wogan_2023} pessimistic case, which requires a $> 5 \times 10^{21}$ kg impact without later ocean vaporization (Figure \ref{fig:time_and_mass}b). In this scenario, the median timing for life's origin is 4.36 Ga with 95\% a confidence interval spanning 3.94 to 4.49 Ga (Figure \ref{fig:time_and_mass}b (i)). Under these assumptions, the life-starting impact is Moneta-sized 31\% of the time (Figure \ref{fig:time_and_mass}b (ii)), which is more probable compared to ``optimistic'' case (Figure \ref{fig:time_and_mass}a (ii)).
